\documentclass[a4paper,10pt]{article}

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[
  top=12mm,
  bottom=12mm,
  left=14mm,
  right=14mm
]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}

% ---------- Hyperref / PDF metadata (ATS-friendly: real text, no link recoloring) ----------
\hypersetup{
  pdftitle={Mohammed Rinshad M I - Full-Stack Software Engineer Resume},
  pdfauthor={Mohammed Rinshad M I},
  pdfsubject={Full-Stack Software Engineer},
  pdfkeywords={React, Next.js, Node.js, Golang, TypeScript, Python, RAG, LLM, Gemini, Groq, Ollama, PostgreSQL, pgvector, Redis, Stripe, Razorpay, Docker, AWS, GitHub Actions, Jest, Playwright},
  colorlinks=false,
  pdfborder={0 0 0}
}

% ---------- Global typography ----------
\linespread{1.05}
\setlength{\parindent}{0pt}
\pagestyle{empty}

% ---------- Section headers (uppercase + full-width rule, parser-friendly) ----------
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}{0em}
  {}[\vspace{1pt}\hrule height 0.8pt]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% ---------- List styling ----------
\setlist[itemize]{
  leftmargin=14pt,
  topsep=2pt,
  itemsep=2pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

% ---------- Helper macros ----------
% Entry row: title (left, bold) + date (right, bold)
\newcommand{\entry}[2]{%
  \noindent\textbf{#1}\hfill\textbf{#2}\par
}

% Tech-stack line under an entry/project
\newcommand{\stack}[1]{%
  {\small\itshape\color{black!72}#1}\par
}

% ---------- Document ----------
\begin{document}

% ===== Header =====
\begin{center}
  {\LARGE\bfseries Mohammed Rinshad M I}\\[3pt]
  {\footnotesize Full-Stack Software Engineer $\vert$ React, Next.js, Node.js, Golang $\vert$ AI/LLM \& Real-Time Systems}\\[4pt]
  {\footnotesize
    Palakkad, Kerala, India \quad\textbullet\quad
    \href{mailto:rinshad803@gmail.com}{rinshad803@gmail.com} \quad\textbullet\quad
    \href{tel:+918848675355}{+91 88486 75355} \\[2pt]
    \href{https://linkedin.com/in/mohd-rinshadmi}{linkedin.com/in/mohd-rinshadmi} \quad\textbullet\quad
    \href{https://github.com/MohdRinshadmi}{github.com/MohdRinshadmi}
  }
\end{center}

% ===== Summary =====
\section{Summary}
Full-Stack Software Engineer with 2.5+ years of experience building and scaling production web and mobile applications using React, Next.js, React Native, Node.js, Express, Golang, MySQL, PostgreSQL, Redis, and AWS.
\vspace{4pt}

Shipped eCommerce, LMS, and AI-powered products end-to-end --- Stripe, PayPal, and Razorpay payment systems, RAG and semantic-search features, and real-time collaboration platforms. Reduced API response times by 35\%, raised Lighthouse performance from 62 to 89, and owned Docker, CI/CD, and Linux/VPS deployments for reliable, monitored releases.

% ===== Key Achievements =====
\section{Key Achievements}
\begin{itemize}
  \item \textbf{Delivered 20+ production features} across eCommerce, LMS, and AI platforms using React, React Native, and Node.js.
  \item \textbf{Reduced API latency by 35\% and raised Lighthouse score from 62 to 89} through query optimization, indexing, code-splitting, and CDN delivery.
  \item \textbf{Processed 2,000+ monthly transactions} via Stripe, PayPal, and Razorpay integrations with webhook-driven order lifecycle management.
  \item \textbf{Shipped LLM-powered features} including RAG, semantic search, streaming chat, and AI workflow automation.
\end{itemize}

% ===== Experience =====
\section{Experience}
\entry{Infinite Open Source Solution LLP --- Software Engineer, Calicut, Kerala}{Nov 2023 -- Present}
\stack{React.js \textbullet\ Node.js \textbullet\ Express.js \textbullet\ MySQL \textbullet\ Sequelize \textbullet\ Redis \textbullet\ Docker \textbullet\ Linux \textbullet\ REST APIs}
\begin{itemize}
  \item \textbf{Migrated the entire codebase from JavaScript to TypeScript} across both web (React) and mobile (React Native) apps, adding full type safety that caught bugs early and made the code easier to maintain.
  \item \textbf{Built a shared TypeScript component and API-contract library} used across React, Next.js, and React Native projects, reducing duplicated code and speeding up feature delivery.
  \item \textbf{Integrated Stripe, PayPal, and Razorpay payment gateways} with webhook-driven order lifecycle management for a production eCommerce platform processing 2,000+ monthly transactions.
  \item \textbf{Architected 40+ RESTful API endpoints} using Express.js and Sequelize ORM with middleware-based input validation, JWT authentication, structured error handling, and SQL query optimization --- reducing average API response time by 35\%.
  \item \textbf{Led frontend migration from Create React App to Vite}, cutting build times from {\raise.17ex\hbox{$\scriptstyle\sim$}}90s to {\raise.17ex\hbox{$\scriptstyle\sim$}}35s (60\%+ reduction) and accelerating developer iteration cycles across a 4-person frontend team.
  \item \textbf{Optimized React rendering, code-splitting, and CDN-based static asset delivery}, improving Lighthouse performance score from 62 to 89 and reducing initial page load time from 3.8s to 2.1s.
\end{itemize}

% ===== Portfolio Projects =====
\filbreak
\section{Portfolio Projects}
Self-initiated projects built to explore production patterns in AI, real-time systems, and cloud-native architecture --- running entirely on free-tier and open-source infrastructure (self-hosted Postgres/Redis, Docker, Gemini/Groq free tiers); no commercial users. Source: \href{https://github.com/MohdRinshadmi}{github.com/MohdRinshadmi}.
\vspace{4pt}

\entry{Cloud-Native IoT Analytics Platform}{2024}
\stack{React \textbullet\ TypeScript \textbullet\ Golang \textbullet\ Gin \textbullet\ GORM \textbullet\ PostgreSQL \textbullet\ Redis \textbullet\ Docker}
\begin{itemize}
  \item \textbf{Architected a cloud-native IoT analytics platform (React + Golang)} with Clean Architecture, repository/\allowbreak service-layer patterns, and dependency injection --- structured as a scalable monorepo separating frontend, backend, infrastructure, and shared modules.
  \item \textbf{Developed RESTful APIs and device-management services} ingesting high-frequency telemetry using Gin, GORM, PostgreSQL, and Redis with structured configuration management and middleware-based request handling.
  \item \textbf{Built reusable frontend infrastructure} with TanStack Query, Zustand, feature-based modules, and type-safe API integrations, reducing UI boilerplate across new dashboards.
  \item \textbf{Containerized backend, database, broker, and supporting services} using Docker Compose, enabling one-command local deployment and consistent development environments.
\end{itemize}

\filbreak
\entry{AI Life Assistant Super App}{2024}
\stack{React \textbullet\ Next.js (App Router, RSC) \textbullet\ Node.js \textbullet\ TypeScript \textbullet\ Python \textbullet\ Gemini API \textbullet\ PostgreSQL + pgvector \textbullet\ Redis}
\begin{itemize}
  \item \textbf{Architected a voice-first AI assistant} with streaming LLM chat, speech-to-text transcription, TTS playback, and tool calling across a React/Next.js Server Components UI and Node.js APIs.
  \item \textbf{Indexed and retrieved knowledge from thousands of embedded documents} using PostgreSQL + pgvector and HNSW indexing, delivering sub-second semantic search relevance.
  \item \textbf{Built Python data-ingestion scripts} for chunking, embedding generation, and batch document indexing feeding the RAG pipeline.
  \item \textbf{Secured the API} with JWT refresh-token rotation and Redis-backed rate limiting.
\end{itemize}

\filbreak
\entry{AI-Powered Real-Time Collaboration Platform}{2023}
\stack{React \textbullet\ Next.js \textbullet\ TypeScript \textbullet\ Node.js \textbullet\ WebSockets \textbullet\ Yjs (CRDT) \textbullet\ PostgreSQL + pgvector \textbullet\ Redis \textbullet\ Docker}
\begin{itemize}
  \item \textbf{Built a CRDT-based collaborative editor using Yjs} with real-time presence, typing indicators, and conflict-free synchronization across multiple concurrent clients.
  \item \textbf{Engineered a stateless WebSocket fan-out server} with channel-based routing and Redis pub/sub to sustain many concurrent editors.
  \item \textbf{Integrated streaming LLM features} for inline summarization and actions on selected text, with JWT/OAuth access control.
  \item \textbf{Wrote end-to-end Playwright tests} covering multi-user editing, reconnection, and conflict-resolution flows for release confidence.
\end{itemize}

\filbreak

% ===== Technical Skills =====
\section{Technical Skills}
\begin{itemize}[label={},leftmargin=0pt,itemsep=2pt]
  \item \textbf{Languages:} TypeScript, JavaScript, Python, Golang, SQL
  \item \textbf{Frontend:} React, Next.js (App Router, Server Components), React Native, Redux Toolkit, Zustand, TanStack Query, Tailwind CSS, Vite
  \item \textbf{Backend \& APIs:} Node.js, Express, Gin, Sequelize ORM, GORM, REST APIs, WebSockets, Redis Pub/Sub, JWT/OAuth
  \item \textbf{Payments:} Stripe, PayPal, Razorpay (webhook-driven order lifecycle)
  \item \textbf{Databases:} PostgreSQL, pgvector (HNSW), MongoDB, MySQL, Redis
  \item \textbf{AI / LLM:} Gemini \& Groq (free tier), Ollama (local LLMs), LangChain, Vercel AI SDK, RAG, Embeddings, Semantic Search, Streaming, Tool / Function Calling
  \item \textbf{Architecture:} Clean Architecture, Repository \& Service-Layer Patterns, Dependency Injection, Monorepo, CRDT (Yjs), Real-Time Systems
  \item \textbf{Cloud \& DevOps:} AWS (free tier), Docker, Docker Compose, GitHub Actions (CI/CD), Nginx, PM2, Linux/VPS
  \item \textbf{Tools:} Git, Playwright, Vitest, Jest, Sentry (free tier), Lighthouse
\end{itemize}

% ===== Education =====
\section{Education}
\entry{BBA, SJES College of Management --- Bangalore North University, Bangalore, India}{June 2019 -- Oct 2022}

\end{document}
